Tables with \textbf{xtable} and \textbf{knitr}

### 2016-08-12 src/ArticleReadyTableGenerate.Rnw
added  pooled stat tests

<<LoadData_and_BasicDataMunge,echo=FALSE,results='hide',warning=FALSE, message=FALSE>>=
# Load Data
library(foreign)
library(dplyr)
library(xtable)
HOME_DIR <- Sys.getenv("HOME")
print(HOME_DIR)
setwd(HOME_DIR)
setwd("./projects/MAS_Score_Analysis")
#setwd( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/"))
#The script gets data from  SPSS files, merges data frames to one data frame
source("./src/MAS_MCIsubtype_analysis.R")
all.df<- droplevels(all.df)

@@

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline
		Diag \T& Gender & Number & \multicolumn{2}{c}{Age (Yrs)} & \multicolumn{2}{c}{YrsEd (Yrs)} \\
		& \B & & Mean & SD & Mean & SD \\ \hline
<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE>>=
  class(summary_table_1.df)<-"data.frame"
  table.out <- xtable(summary_table_1.df)
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE)
  @

@@

<<Pooled_Stat_Tests>>=
 side =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(1,2,1,3,1,4,1,5,2,3,2,4,4,5,dim = c(2,7)))

  cond_1_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_1,"_wave1_pooled_antsy.txt"))
  cond_2_fileh <- open(file = paste0(DATA_DIR,"/",side,'_',region,"_",cond_2,"_wave1_pooled_antsy.txt"))

>>>>

<<LoadData_and_BasicDataMunge,echo=FALSE,results='hide',warning=FALSE, message=FALSE,cache=FALSE>>=
# Load Data
library(foreign)
library(dplyr)
library(xtable)
HOME_DIR <- Sys.getenv("HOME")
print(HOME_DIR)
opts_knit$set(root.dir=paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/",sep="",collapse=""))
#setwd("./projects/MAS_Score_Analysis")
#setwd( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/"))
#The script gets data from  SPSS files, merges data frames to one data frame
source( paste0(Sys.getenv("HOME"),"/projects/MAS_Score_Analysis/","./src/MAS_MCIsubtype_analysis.R",sep="",collapse=""))
all.df<- droplevels(all.df)

@@

\begin{table}[t]
  \centering
	\begin{tabular}{rrrrrrr}
		\hline
		Diag \T& Gender & Number & \multicolumn{2}{c}{Age (Yrs)} & \multicolumn{2}{c}{YrsEd (Yrs)} \\
		& \B & & Mean & SD & Mean & SD \\ \hline
<<Table_1_summarystats, results='asis', eval=TRUE,echo=FALSE,cache=FALSE>>=
  class(summary_table_1.df)<-"data.frame"
  table.out <- xtable(summary_table_1.df)
  print.xtable(table.out, only.contents=TRUE, include.rownames=FALSE,include.colnames=FALSE)
  @

@@

<<Pooled_Stat_Tests>>=
  DATA_DIR = "./data/pooled_analysis/"
  sides =  c("lh","rh")
  regions = c("itg","mtg","stg","antcing","postcing")
  conditions  = c("normal","aMCI","amdMCI","nMCI","nmdMCI")
  comparisons = t(array(c(1,2,1,3,1,4,1,5,2,3,2,4,4,5),dim = c(2,7)))

  pool_stat_tests_all_regions_sides<- list(lh = NULL, rh = NULL)
  for ( side in sides) {
    pool_stat_tests_all_regions_sides[[side]] = list()
    for ( region in regions ) {
      pooled_stats_list = list()

      #read the pooled files 
      for (i in 1:5) {
        cond_fileh <- paste(DATA_DIR,"/",side,'_',region,"_", conditions[i], 
                            "_wave1_pooled_antsy.txt", sep="", collapse ="")
        print (cond_fileh)
        if (! file.exists(cond_fileh)) {
          print (paste0( cond_fileh,
                         " does not exist",sep="",collapse="") )
        }
        pooled_stats <-read.table(file=cond_fileh, nrows = 2.5E6, colClasses = "numeric")
        print (str(pooled_stats_list))
        if ( is.data.frame(pooled_stats_list) ) {
          pooled_stats <- pooled_stats[,1]
        }
        pooled_stats_list <-c(pooled_stats_list,list(pooled_stats))

      }
      pool_stat_tests_all_regions_sides[[side]] <-c(pool_stat_tests_all_regions_sides[[side]], list(pooled_stats_list)) 
      #run the stat tests for the 7 pair comparisons. We may want to limi
      pooled_test_result<-list()
      for ( i in 1:7 ) {
        pooled_test_result <- c(pooled_test_result,list=list())
      }

      p_values<-list(mwu.test=rep(0,7), ks.test = rep(0,7), kolmog.test = rep(0,7))
      for ( i in 1:7 ) {
        cond_1 = comparisons[i,1]
        cond_2 = comparisons[i,2]

        pooled_test_result[[i]] <- ks.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                                           alternative="t",exact = NULL)
        p_values$ks.test[i] <-pooled_test_result[[i]]$p.value

        pooled_test_result[[i]] <- wilcox.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],
                                               alternative="t",exact = FALSE,
                                               correct = FALSE)
        p_values$mwu.test[i] <-pooled_test_result[[i]]$p.value
        pooled_test_result[[i]] <- t.test(pooled_stats_list[[cond_2]], pooled_stats_list[[cond_1]],    
                                           alternative = "t",mu = 0, paired = FALSE, 
                                           var.equal = FALSE, conf.level = 0.95)

        p_values$welcht.test[i] <-pooled_test_result[[i]]$p.value
      }
      pool_stat_tests_all_regions_sides[[side]] <- c(pool_stat_tests_all_regions_sides[[side]],list(pooled_test_result) )
    }
    names(pool_stat_tests_all_regions_sides[[side]]) <- regions
  }
